Capstone Movielens Report

### 2025-05-08 reports/capstone-movielens-report.draft4.tex
Draft report updated.

\title{Capstone Movielens Report}
\author{Azamat Kurbanaev}
\date{2025-05-08}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-20-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-24-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-27-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-28-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-47-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-52-1.pdf}

@@

\subsubsection{Taking into account User
Effect}\label{taking-into-account-user-effect}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-55-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-60-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-62-1.pdf}

@@

\begin{noteblock}
The full source code of the \emph{User Effect Model RMSE} computation is
available in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L655}{Computing
the RMSE taking into account User Effect} section of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
script on \emph{GitHub}.

@@

\subsubsection{Taking into account Movie
effects}\label{taking-into-account-movie-effects}

@@

In
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movie-effects}{Section
\emph{23.5 Movie effects} of the \emph{Course Textbook}} the author
draws our attention to the fact that some movies are generally rated
higher than others. He also explains that~a linear model with a
\emph{treatment effect} \(\beta_j\) for each movie can be used in this
case, which can be interpreted as movie effect or the difference between
the average ranking for movie \(j\) and the overall average \(\mu\):

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{user\_and\_movie\_effects\_rmse }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(a)), }\AttributeTok{a =}\NormalTok{ a), }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{left\_join}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(}\AttributeTok{movieId =} \FunctionTok{as.integer}\NormalTok{(}\FunctionTok{names}\NormalTok{(b)), }\AttributeTok{b =}\NormalTok{ b), }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b)) }\SpecialCharTok{|\textgreater{}}  
    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(resid)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{rmse}\NormalTok{()}

\FunctionTok{print}\NormalTok{(user\_and\_movie\_effects\_rmse)}
\end{Highlighting}
\end{Shaded}

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-72-1.pdf}

>>>>

\title{Capstone Movielens Report}
\author{Azamat Kurbanaev}
\date{2025-05-09}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-15-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-18-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-19-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-38-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-43-1.pdf}

@@

\subsubsection{User Effect Model}\label{user-effect-model}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-46-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-51-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-53-1.pdf}

@@

\begin{noteblock}
The full source code of the \emph{User Effect Model RMSE} computation is
available in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L655}{Compute
RMSE for User Effect Model} section of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
script on \emph{GitHub}.

@@

\subsubsection{User+Movie Effect (UME)
Model}\label{usermovie-effect-ume-model}

@@

In
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movie-effects}{23.5
Movie effects} section of the \emph{Course Textbook} the author draws
our attention to the fact that some movies are generally rated higher
than others. He also explains that a linear model with a \emph{treatment
effect} \(\beta_j\) for each movie can be used in this case, which can
be interpreted as movie effect or the difference between the average
ranking for movie \(j\) and the overall average \(\mu\):

@@

Inspired by this idea, a few support functions were developed by the
author of this report, which we will use for our further analysis.

\paragraph{UME Model: Support
Functions}\label{ume-model-support-functions}

\begin{noteblock}
The full source code of the functions described in this section is
available in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L1}{User+Movie
Effect Model Functions} section of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
script on \emph{GitHub}.

\subparagraph{\texorpdfstring{\texttt{train\_user\_movie\_effect}
Function}{train\_user\_movie\_effect Function}}\label{train_user_movie_effect-function}

We use this function to build and train our model using the
\texttt{train\_set} dataset:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{train\_user\_movie\_effect }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(train\_set, }\AttributeTok{lambda =} \DecValTok{0}\NormalTok{)\{}
  \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.na}\NormalTok{(lambda)) \{}
    \FunctionTok{stop}\NormalTok{(}\StringTok{"Function: train\_user\_movie\_effect}
\StringTok{\textasciigrave{}lambda\textasciigrave{} is \textasciigrave{}NA\textasciigrave{}"}\NormalTok{)}
\NormalTok{  \}}

\NormalTok{  UM.effect }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{left\_join}\NormalTok{(edx.user\_effect, }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}}\NormalTok{ (mu }\SpecialCharTok{+}\NormalTok{ a)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{b =} \FunctionTok{mean\_reg}\NormalTok{(resid, lambda), }\AttributeTok{n =} \FunctionTok{n}\NormalTok{())}

  \FunctionTok{stopifnot}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(}\FunctionTok{mean}\NormalTok{(UM.effect}\SpecialCharTok{$}\NormalTok{b)))}
\NormalTok{  UM.effect}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{noteblock}
The function described above accepts the \texttt{lambda} parameter,
which we will need later for the \emph{Regularization} method. We also
use the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L63}{mean\_reg}
function call, which we will also need for the \emph{Regularization}. We
will explain that later in the {[}Regularization Method{]} section. For
now, we omit the \texttt{lambda} parameter, accepting its default value
\texttt{lambda\ =\ 0}. In this case, the \texttt{mean\_reg} function is
equivalent to the simple \texttt{mean} one.

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# Regularization {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{mean\_reg }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(vals, }\AttributeTok{lambda =} \DecValTok{0}\NormalTok{, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)\{}
  \ControlFlowTok{if}\NormalTok{ (}\FunctionTok{is.na}\NormalTok{(lambda)) \{}
    \FunctionTok{stop}\NormalTok{(}\StringTok{"Function: mean\_reg}
\StringTok{\textasciigrave{}lambda\textasciigrave{} is \textasciigrave{}NA\textasciigrave{}"}\NormalTok{)}
\NormalTok{  \}}

  \FunctionTok{names}\NormalTok{(lambda) }\OtherTok{\textless{}{-}} \ConstantTok{NULL}
\NormalTok{  sums }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(vals, }\AttributeTok{na.rm =}\NormalTok{ na.rm)}
\NormalTok{  N }\OtherTok{\textless{}{-}} \FunctionTok{ifelse}\NormalTok{(na.rm, }\FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(vals)), }\FunctionTok{length}\NormalTok{(vals))}
\NormalTok{  sums}\SpecialCharTok{/}\NormalTok{(N }\SpecialCharTok{+}\NormalTok{ lambda)}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subparagraph{\texorpdfstring{\texttt{train\_user\_movie\_effect.cv}
Function}{train\_user\_movie\_effect.cv Function}}\label{train_user_movie_effect.cv-function}

We use the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L17}{train\_user\_movie\_effect.cv}
function to build and train our model using the
\texttt{5-Fold\ Cross\ Validation} method. Below, we provide the most
important part of the code of that function:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{train\_user\_movie\_effect.cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(}\AttributeTok{lambda =} \DecValTok{0}\NormalTok{)\{}
\CommentTok{\# ...}
\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
\NormalTok{  user\_movie\_effects\_ls }\OtherTok{\textless{}{-}} \FunctionTok{lapply}\NormalTok{(edx\_CV, }\ControlFlowTok{function}\NormalTok{(cv\_fold\_dat)\{}
\NormalTok{    cv\_fold\_dat}\SpecialCharTok{$}\NormalTok{train\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{train\_user\_movie\_effect}\NormalTok{(lambda)}
\NormalTok{  \})}
  \FunctionTok{put\_end\_date}\NormalTok{(start)}
  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: train\_user\_movie\_effect.cv:}
\StringTok{User+Movie Effect list have been computed"}\NormalTok{)}

\NormalTok{  user\_movie\_effects\_united }\OtherTok{\textless{}{-}} \FunctionTok{union\_cv\_results}\NormalTok{(user\_movie\_effects\_ls)}

\NormalTok{  user\_movie\_effect }\OtherTok{\textless{}{-}}\NormalTok{ user\_movie\_effects\_united }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{group\_by}\NormalTok{(movieId) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{summarise}\NormalTok{(}\AttributeTok{b =} \FunctionTok{mean}\NormalTok{(b), }\AttributeTok{n =} \FunctionTok{mean}\NormalTok{(n))}
  \CommentTok{\# ...}
\NormalTok{  user\_movie\_effect}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{noteblock}
Here we use the function call
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R\#L432}{union\_cv\_results},
which is defined in the script
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R}{common-helper.functions.R},
to aggregate the ``cross-validation'' results.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{union\_cv\_results }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data\_list) \{}
\NormalTok{  out\_dat }\OtherTok{\textless{}{-}}\NormalTok{ data\_list[[}\DecValTok{1}\NormalTok{]]}

  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{2}\SpecialCharTok{:}\NormalTok{CVFolds\_N)\{}
\NormalTok{    out\_dat }\OtherTok{\textless{}{-}} \FunctionTok{union}\NormalTok{(out\_dat, }
\NormalTok{                     data\_list[[i]])}
\NormalTok{  \}}

\NormalTok{  out\_dat}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_MSE}
Function}{calc\_user\_movie\_effect\_MSE Function}}\label{calc_user_movie_effect_mse-function}

The code of the function
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L55}{calc\_user\_movie\_effect\_MSE}
defined in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
script to calculate the \texttt{MSE} of the \texttt{UME\ Model} for the
given \texttt{Test\ Set} is provided below:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{calc\_user\_movie\_effect\_MSE }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(test\_set, um\_effect)\{}
\NormalTok{  mse.result }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{left\_join}\NormalTok{(edx.user\_effect, }\AttributeTok{by =} \StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{left\_join}\NormalTok{(um\_effect, }\AttributeTok{by =} \StringTok{"movieId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{resid =}\NormalTok{ rating }\SpecialCharTok{{-}} \FunctionTok{clamp}\NormalTok{(mu }\SpecialCharTok{+}\NormalTok{ a }\SpecialCharTok{+}\NormalTok{ b)) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{pull}\NormalTok{(resid) }\SpecialCharTok{|\textgreater{}} \FunctionTok{mse}\NormalTok{()}

  \FunctionTok{stopifnot}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(mse.result))}
\NormalTok{  mse.result}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_MSE.cv}
Function}{calc\_user\_movie\_effect\_MSE.cv Function}}\label{calc_user_movie_effect_mse.cv-function}

The code of the function
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L72}{calc\_user\_movie\_effect\_MSE.cv}
defined in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
script to calculate the \texttt{5-Fold\ Cross\ Validation} MSE result of
the \texttt{UME\ Model} is provided below:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{calc\_user\_movie\_effect\_MSE.cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(um\_effect)\{}
  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: user\_movie\_effects\_MSE.cv:}
\StringTok{Computing the RMSE taking into account User+Movie Effects..."}\NormalTok{)}
\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
\NormalTok{  user\_movie\_effects\_MSEs }\OtherTok{\textless{}{-}} \FunctionTok{sapply}\NormalTok{(edx\_CV, }\ControlFlowTok{function}\NormalTok{(cv\_fold\_dat)\{}
\NormalTok{    cv\_fold\_dat}\SpecialCharTok{$}\NormalTok{validation\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{calc\_user\_movie\_effect\_MSE}\NormalTok{(um\_effect)}
\NormalTok{  \})}
  \FunctionTok{put\_end\_date}\NormalTok{(start)}

  \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Function: user\_movie\_effects\_MSE.cv:}
\StringTok{MSE values have been plotted for the \%1{-}Fold Cross Validation samples."}\NormalTok{, }
\NormalTok{           CVFolds\_N)}

  \FunctionTok{mean}\NormalTok{(user\_movie\_effects\_MSEs)}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_RMSE}
Function}{calc\_user\_movie\_effect\_RMSE Function}}\label{calc_user_movie_effect_rmse-function}

The code of the function
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L51}{calc\_user\_movie\_effect\_RMSE}
defined in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
script to calculate the \texttt{RMSE} of the \texttt{UME\ Model} for the
given \texttt{Test\ Set} is provided below:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{calc\_user\_movie\_effect\_RMSE }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(test\_set, um\_effect)\{}
\NormalTok{  mse }\OtherTok{\textless{}{-}}\NormalTok{ test\_set }\SpecialCharTok{|\textgreater{}} \FunctionTok{calc\_user\_movie\_effect\_MSE}\NormalTok{(um\_effect)}
  \FunctionTok{sqrt}\NormalTok{(mse)}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subparagraph{\texorpdfstring{\texttt{calc\_user\_movie\_effect\_RMSE.cv}
Function}{calc\_user\_movie\_effect\_RMSE.cv Function}}\label{calc_user_movie_effect_rmse.cv-function}

The code of the function
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R\#L65}{calc\_user\_movie\_effect\_RMSE.cv}
defined in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R}{UM-effect.functions.R}
script to calculate the \texttt{5-Fold\ Cross\ Validation} RMSE result
of the \texttt{UME\ Model} is provided below:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{calc\_user\_movie\_effect\_RMSE.cv }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(um\_effect)\{}
\NormalTok{  user\_movie\_effects\_MSE }\OtherTok{\textless{}{-}} \FunctionTok{calc\_user\_movie\_effect\_MSE.cv}\NormalTok{(um\_effect)}
\NormalTok{  um\_effect\_RMSE }\OtherTok{\textless{}{-}} \FunctionTok{sqrt}\NormalTok{(user\_movie\_effects\_MSE)}
  \FunctionTok{put\_log2}\NormalTok{(}\StringTok{"Function: user\_movie\_effects\_RMSE.cv:}
\StringTok{\%1{-}Fold Cross Validation ultimate RMSE: \%2"}\NormalTok{, CVFolds\_N, um\_effect\_RMSE)}
\NormalTok{  um\_effect\_RMSE}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\paragraph{Model Building}\label{model-building}

\begin{noteblock}
The full source code of builing and training the current model is
available in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R\#L721}{Model
building: User+Movie Effect} section of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R}{capstone-movielens.main.R}
script on \emph{GitHub}.

Below, we provide the most important code of the training our model
using the \texttt{5-Fold\ Cross\ Validation} method:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{  cv.UM\_effect }\OtherTok{\textless{}{-}} \FunctionTok{train\_user\_movie\_effect.cv}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{par}\NormalTok{(}\AttributeTok{cex =} \FloatTok{0.7}\NormalTok{)}
\FunctionTok{hist}\NormalTok{(cv.UM\_effect}\SpecialCharTok{$}\NormalTok{b, }\DecValTok{30}\NormalTok{, }\AttributeTok{xlab =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[$\textbackslash{}hat\{beta\}\_\{j\}$)]\textquotesingle{}}\NormalTok{),}
     \AttributeTok{main =} \FunctionTok{TeX}\NormalTok{(r}\StringTok{\textquotesingle{}[Histogram of $\textbackslash{}hat\{beta\}\_\{j\}$]\textquotesingle{}}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-64-1.pdf}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{cv.UM\_effect.RMSE }\OtherTok{\textless{}{-}} \FunctionTok{calc\_user\_movie\_effect\_RMSE.cv}\NormalTok{(cv.UM\_effect)}

\NormalTok{RMSEs.ResultTibble.UME }\OtherTok{\textless{}{-}}\NormalTok{ RMSEs.ResultTibble.UE }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{RMSEs.AddRow}\NormalTok{(}\StringTok{"User+Movie Effect Model"}\NormalTok{, cv.UM\_effect.RMSE)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{RMSE\_kable}\NormalTok{(RMSEs.ResultTibble.UME)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{35em}>{\centering\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{50em}}
\toprule
\textbf{Method} & \textbf{RMSE} & \textbf{Comment}\\
\midrule
Project Objective & 0.8649000 & \\
Overall Mean Rating Model & 1.0603462 & \\
User Effect Model & 0.9697962 & \\
User+Movie Effect Model & 0.8732081 & \\
\bottomrule
\end{longtable}

@@

\subparagraph{`` Function}\label{function}

\subparagraph{`` Function}\label{function-1}

\subparagraph{`` Function}\label{function-2}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-83-1.pdf}
